MLH1 Data Report

### 2019-08-30 doc/Main_Report.rmd
updating list of mice to finish

#load main data file
load(file="data/MLH1/MLH1_data_setup_8.15.19.RData")

load(file="data/MetaData.RData")

@@

## Research Description

@@

#### Description of Report

@@

#### Discription of quantification process

@@

@@

# Mice

## Missing Mice

@@

@@

@@

### Histograms of Mouse Ages

@@

#### Is there an age effect?

@@

```{r}
#run a age effect linear regression!

@@

#make sure the right dataset 
male.data <- AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$sex.y == "male") & (AP_mouse_table_w.Ages$category.y != "other"),]

@@

male.data <- add_subsp(male.data)

age.effect.plot <- ggplot(male.data, aes(y=mean_co, x=age.weeks, color=strain.y))+geom_point()+ ylim(c(15,39))+
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+ggtitle("Age Effect on CO mean")+facet_wrap(~subsp.y)

#todo add line to strain.y

@@

#### Initial Patterns from MLH1 distributions

```{r first.boxplots, echo=FALSE, fig.align='center'}
#what?
#MLH1_data <- MLH1_data[MLH1_data$strain]

@@

#can't re-order the miceagg
ff <- ggplot(MLH1_data[order(MLH1_data$strain), ], 
             aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue", "coral4","coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey", 
        "grey","grey","grey",  "grey","grey","grey" )) +
 ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+5)) + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by strain") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" )) +
  ylim( c( (min(MLH1_data$adj_nMLH1.foci)-3), (max(MLH1_data$adj_nMLH1.foci)+5)) )

@@

#these plot currently look bad

@@

```{r, histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
#consider making distribution with quality considered...

histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38))
histM <- histM + geom_histogram(stat = "bin", binwidth = 1)
histM <- histM + facet_wrap(~ category)
histM
```

` r knitr_exit()`

#### Assesment of Quality Scores

```{r high qual, fig.caption="boxplots of MLH1 distributions", fig.height=5, fig.width=5, echo=FALSE, warnings=FALSE, include=FALSE}

@@

```{r, passing mice, echo=FALSE}
q_cutoff_table <- ddply(MLH1_data, .(mouse), summarise,
                        total =  length(adj_nMLH1.foci),
                        q5 = sum(as.numeric(quality) >= 4, na.rm = TRUE ), 
                        above5 = sum(as.numeric(quality) <= 4, na.rm = TRUE )
                       # q_l3 = sum(as.numeric(as.numeric(quality)) <= 4, na.rm = TRUE )
)
#q_cutoff_table
passed_mice <- as.vector(q_cutoff_table[q_cutoff_table$above5 > 15,]$mouse)

@@

#### Comparison of MLH1 distributions

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
#high_qual_boxplot
#not sure why order got messed up again...
```

After taking the data from 2 highest cell quality, some but not all mouse means converge. For some mice (mostly female) the majority of cells are excluded. This is especially true for PWD and WSB females.

#### Tests for quality and nMLH1 foci number

##### Effects of quality

@@

```{r, scatter plots of nMLH1 by score, echo=FALSE, fig.cap="MLH1 means across quality scores"}
#make lattice / plots seperated by strain and sex
#facet

@@

#### Assessing the Distributions by mouse

@@

```{r, echo=FALSE, message=FALSE, results='hide', warning=TRUE}
### to integrate 'pass'/fail
### this should be in setup data

#quant_status (this isn't saving)
#for(i in 1:length(MLH1_data$mouse)){
#  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
#}

#what is the purpose of this block
#df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#df_list <- df_list[ -c(7,16,22) ]

#7: PERC male, (14:CAST female, fake data) 16:HMI female, 22 other
#

#df list, is a list of df's which were split() from BIG df by category
#df_list 
#o=0
#i=0

#MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
#for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
#  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
#  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
 #                      mouse_nMLH1 = mean(adj_nMLH1.foci)
#  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
#  for(o in 1:length(df_list[[i]]$Original.Name)){
#    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == #sub_mouse_means$mouse) ]
#        }
#}

#plot_list = list()
#for (h in 1:length(df_list)) {
#  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ #geom_jitter(aes(y= adj_nMLH1.foci, x= quality))
  # +   geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5)
#  + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL)

# +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
#  
#  plot_list[[h]] =   pf
#}

#orig
#plot_list = list()
#for (h in 1:length(df_list)) {
#  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
#  pf <- pf +geom_rect(data = df_list[[h]], aes(fill=quant_status), xmin=-100, xmax=100, #ymin=-100, ymax=100, alpha=0.005)

#    pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
#  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
#  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") #+

#    scale_fill_manual(values=alpha(c("red"), .005), breaks=NULL)

    #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
#  plot_list[[h]] =   pf
#}
#can't change the alpha/transparency of the red rec

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
#geom_hline(aes(yintercept = med, group = gr), colour = 'red')
#
#for (gg in 1:length(plot_list) ){
#  show(plot_list[gg])
  #invisible(lapply(obj, function(x) plot(x,main="some plot")))
#}
```

Making all of these scatter plots, allows us to look at the whole distributions of the data for each mouse. The distance of the red line from the black could be a indicator of slides or mice with slide specific technical noise.

@@

>>>>

#load main data file
load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")

#load(file="data/MetaData.RData") #this was replacing most updated data file

@@

# Research Description

@@

## Description of Report

@@

## Discription of quantification process

@@

Definition of passed quantified ect.

@@

*What were guidlines for quantification of lower quality cells / faint foci?*

-Count foci that look like other foci in the image.

## Missing Mice, finishing dataset

*Which mice are remaining and at what stage?*

@@

passed quantified - quantified mice (with enough cells)
total quantified -- all mice which have been (includes fail and passing mice)

non-quantified mice -- dissected mice / slides that haven't been quantified yet (all stained, but without image directory)

non-imaged -- mice without images, (might be stained and unstained)

@@

should I break down the categories into sex and strain?

@@

# Tests of dataset

Main metric is mean CO count per mouse. Assess the quality of this data with the following tests

*age effects* (male, maternal age)

*litter effect*

*mouse room effect* (Charmony, MSC)

*quantification repeatability*

*spread batch and staining effects*

*power analysis on number of cells*

*time of year effect (on spread)*

These aspects will be analyzed with a linear models on subsets of data (within category)

## Repeatability of Human quantification

*What is the Error in quantification across humans?*

A general ancedote is that if the quality of the cell staining / image is high, then the repeatability is near 100%. (useing some of Beth's data)

There is a subset of data which has been counted mulitple times -- use that to test the repeatbility.

```{r quant.repeatability, echo=FALSE}

## Age Effect

@@

 Is there an age effect?

@@

```{r age.effect.model}
#run a age effect linear regression!

@@

#make sure the right dataset 
male.data <- AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$sex.y == "male") & (AP_mouse_table_w.Ages$category.y != "other"),]
#remove NAs

@@

age.effect.plot <- ggplot(male.data, aes(y=mean_co, x=age.weeks, color=strain.y))+geom_point()+ ylim(c(15,39))+
  geom_smooth(method='lm',alpha=0.1, size=0, span=0.5 )+ggtitle("Age Effect on CO mean")+facet_wrap(~subsp.y)
age.effect.plot
#todo add line to strain.y

@@

#### Materinal Age effect

```{r mat.age.effect, echo=FALSE}
#compile data from female (and male?) mice with maternal ages.

#start making a general linear model...? for mouse averages

### litter effect?

## Spread and Stain Effects

*month dissected*

*staining batches*

## Room effect (envioronment)

3 different rooms used to house mice. This will be tested in X manner.

## cell number (power analysis results)

# Initial Results

```{r first.boxplots, echo=FALSE, fig.align='center'}

@@

#never make boxplot with mouse on X. mouse level boxplots should be faceted by subspecies 
#can't re-order the miceagg
#ff <- ggplot(MLH1_data[order(MLH1_data$strain), ], 
#             aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
#        axis.text.x=element_blank(),
#        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue", #"coral4","coral1", "#E69F00","red", "red4", "red3","purple","grey1", "grey", 
#        "grey","grey","grey",  "grey","grey","grey" )) +
# ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+5)) + facet_wrap(species~ sex, scales="free")
#don't show M.musculus by mouse

#order MLH1_data by strain!!

ff2 <- ggplot(MLH1_data[MLH1_data$species == "M.musculus", ])+
  geom_boxplot(aes(x = as.character(mouse), y = adj_nMLH1.foci, fill= strain,alpha=0.5) )+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue", "coral4","coral1", "#E69F00","red", "red3", "red4","orange","yellow", "yellow3", 
        "green","green4","grey",  "grey","grey","grey" )) +
 ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+3)) + 
  facet_grid(subsp~ sex, scales="free_x")#scales="free_y"
#this is ok except for the set placement of mice on x axis
#if the full dataset was ordered correctly, this would kinda fix it

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot(aes(alpha=0.5))  + ggtitle("Boxplots of MLH1 distributions by strain") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey","green", "purple","grey1","grey","white", "blue","orange" )) +
  ylim( c( (min(MLH1_data$adj_nMLH1.foci)-3), (max(MLH1_data$adj_nMLH1.foci)+5)) )

@@

#these plot currently look bad
ss
```

*What is the initial picture of Heterochiasmy across mouse strains?*

For the strain level plots
  -facet,sex by species

*Are the MLH1 distributions close to normal?*

```{r, MLH1.histogram, echo=FALSE, fig.caption= "histograms", warning=FALSE, fig.align='center'}
#consider making distribution with quality considered...

gg <- data.frame(weight=rep(x,nrow(df)),df)
gg$y <- with(gg,dnorm(x,mean,sd))
gg$y <- gg$y * aggregate(weight~sex, weight,length)$weight * diff(range(weight$weight))/30

mean.MLH1.obs <- ddply(.data=MLH1_data, 
                 .(category),
                 summarize, 
                 mean.MLH1 = mean(adj_nMLH1.foci),
                 var.MLH1 = var(adj_nMLH1.foci)
)

histM <- ggplot(MLH1_data,(aes(adj_nMLH1.foci))) + xlim(c(16, 38)) + geom_histogram(stat = "bin", binwidth = 1) + facet_wrap(~ category)+ggtitle("Pooled Cell Histograms")+
  geom_line(data=mean.MLH1.obs, aes(y=mean.MLH1.obs$mean.MLH1))

  geom_smooth(method = lm, se = FALSE)

  geom_smooth(method = lm, formula = mean.MLH1.obs$mean.MLH1 ~ mean.MLH1.obs$category, se = FALSE)

histM

#if i'm testing normalge

#function = glm(y ~ x, family = poisson)
#add Poission curve behind
#geom_smooth(method = lm, formula = y ~ splines::bs(x, 3), se = FALSE)

#not sure how to add Expected poisson curve

@@

(most all distributions are close to normal)

How do these compare to Poission? (mean == variance)
I should make 'expected' distributions behind these.

### Assesment of Quality Scores

```{r high.qual, fig.caption="boxplots of MLH1 distributions", fig.height=5, fig.width=5, echo=FALSE, warnings=FALSE, include=FALSE}

@@

```{r, passing.mice, echo=FALSE}
q_cutoff_table <- ddply(MLH1_data, .(mouse), summarise,
                        total =  length(adj_nMLH1.foci),
                        q5 = sum(as.numeric(quality) >= 4, na.rm = TRUE ), 
                        above5 = sum(as.numeric(quality) <= 4, na.rm = TRUE )
                       # q_l3 = sum(as.numeric(as.numeric(quality)) <= 4, na.rm = TRUE )
)
#q_cutoff_table
passed_mice <- as.vector(q_cutoff_table[q_cutoff_table$above5 > 15,]$mouse)

@@

*Answer to questions*

@@

```{r, scatter.plots.of.nMLH1.by.score, echo=FALSE, fig.cap="MLH1 means across quality scores"}
#make lattice / plots seperated by strain and sex
#facet

@@

####Distributions by mouse

*Is there mouse level MLH1 quality score bias?*

@@

below are code chuncks that make a big dfs of CO.count by quality score plot. The code has been commented out, and moved to it's own doc.

```{r mouse.specific.Qplot, echo=FALSE, message=FALSE, results='hide', warning=TRUE, include=FALSE, eval=FALSE}
### to integrate 'pass'/fail
### this should be in setup data

#mice that don't have female data will break the chain-loop
#MOLF female, HMI, CZECH female, CAROLI female, Tom male

#instead of adding fake data, remove the categories from list

#filler_data_MOLF.f = c("BatchX", "1jan19_fake_MOLF_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_MOLF_f1_sp1_rev.tif",
#                       "fake_MOLF_f1", "MOLF female", "MOLF","female","Musc", "20","")
#filler_data_HMI.f = c("BatchX", "1jan19_fake_HMI_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_HMI_f1_sp1_rev.tif",
#                       "fake_HMI_f1", "HMI female", "HMI","female","Cast", "20","")
#filler_data_CZECH.f = c("BatchX", "1jan19_fake_CZECH_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_CZECH_f1_sp1_rev.tif",
#                       "fake_CZECH_f1", "CZECH female", "CZECH","female","Musc", "20","")
#filler_data_CAROLI.f = c("BatchX", "1jan19_fake_CAROLI_f1_sp1", "99999", "3","20","20","","","","","","1jan19_fake_CAROLI_f1_sp1_rev.tif",
#                       "fake_CAROLI_f1", "CAROLI female", "CAROLI","female","Caroli", "20","")
#MLH1_data_table <- rbind(MLH1_data, filler_data_MOLF.f,filler_data_HMI.f,filler_data_CZECH.f,filler_data_CAROLI.f)#error from dataset thing

pass_mice <- c("28sep18_CZECH_m3","26oct18_MOLF_m1","22jun15_G_m2")

#this loop makes a quant_status col for a list of mice
for(i in 1:length(MLH1_data$mouse)){
  MLH1_data$quant_status[i] <- ifelse( is.element(MLH1_data$mouse[i], pass_mice), "pass", NA)
}

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(7,12,14,18,20,21,22,24,26,28,30) ]

#7 PERC, 12 MOLF female, 
#

#df list, is a list of df's which were split() from BIG df by category
df_list 
o=0
i=0

MLH1_data$quant_status <- as.factor(MLH1_data$quant_status)

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                      mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(data = df_list[[h]], aes(colour = factor(Batch)), width = 0.25)+ 
    geom_jitter(aes(y= adj_nMLH1.foci, x= quality)) + 
    geom_rect(data = df_list[[h]], aes(fill=as.factor(quant_status)), alpha=0.5, xmin=-100, xmax=100, ymin=-100, ymax=100)+
    facet_wrap(~ mouse, drop = TRUE) + 
    geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +scale_fill_manual(values=c(NA, "red"), breaks=NULL) +    geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  #theme(plot.background = element_rect(fill = "green")) #theme for indiviual mice, 
  #make an empty ggplot? for missing data

  plot_list[[h]] =   pf
}

#orig (I think this is the same as above)
#plot_list = list()
#for (h in 1:length(df_list)) {
#  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
#  pf <- pf +geom_rect(data = df_list[[h]], aes(fill=quant_status), xmin=-100, xmax=100, ymin=-100, ymax=100, alpha=0.005)

#    pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
#  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
#  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") +

 #   scale_fill_manual(values=alpha(c("red"), .005), breaks=NULL) +

    #theme for indiviual mice, 
#theme(plot.background = element_rect(fill = "green"))
#  plot_list[[h]] =   pf
#}
#can't change the alpha/transparency of the red rec

@@

```{r show.plots, echo=FALSE, message=FALSE,results='hide', warning=FALSE, include=FALSE, eval=FALSE}
geom_hline(aes(yintercept = med, group = gr), colour = 'red')
#no plot is made that goes in the list -- so it can't be shown
for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
 # invisible(lapply(obj, function(x) plot(x,main="some plot")))
}

#this stops at MSM
```

The mouse specific scatter plots aren't show because there are too many. (but they should be used for investigating specific mice).
Making all of these scatter plots, allows us to look at the whole distributions of the data for each mouse. The distance of the red line from the black could be a indicator of slides or mice with slide specific technical noise.

@@

# Research Questions

*-which strain has highest HetC?*

Start thinking of the direction for analysis

## within mouse

### female and male comparison

## within category (strain)

```{r HetC.plot, echo=FALSE,  fig.width=10, fig.height=5}
no_female <- c("HMI", "SKIVE", "CZECH", "MOLF", "CAROLI", "TOM","AST")

MixedModel_CO_data <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$strain.x != "other",]
CO_data_HetC_w.old <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$strain.x != "other",]
CO_data_HetC_w.old <- CO_data_HetC_w.old[ ! CO_data_HetC_w.old$strain.x %in% no_female, ]
CO_data_HetC_w.old <- CO_data_HetC_w.old[!(is.na(CO_data_HetC_w.old$Nmice) | CO_data_HetC_w.old$Nmice==""), ]

MixedModel_CO_data <- MixedModel_CO_data[MixedModel_CO_data$age.weeks < 15,]

MixedModel_CO_data <- MixedModel_CO_data[!(is.na(MixedModel_CO_data$mouse) | MixedModel_CO_data$mouse==""), ]

MixedModel_CO_data <- MixedModel_CO_data[ ! MixedModel_CO_data$strain.x %in% no_female, ]

kuku <- ggplot(MixedModel_CO_data, aes(y=mean_co, x=mouse, color=sex.y))+geom_point()+facet_wrap(~strain.x)

bubu <- ggplot(data=CO_data_HetC_w.old)+geom_point(aes(y=mean_co, x=mouse, color=sex.x))+facet_wrap(~strain.x)

#add titles
#use multiplot
#remove X axis

multiplot(kuku,bubu, cols=2)
```

### female and male comparison

## Subspecies level comparison

Initial results indicate that male MLH1 counts have less variance within subspecies but more between subspecies compared to female data.

*Does this hold up with the full data set?*
*What's the best visualization for these questions?*

Main focus is contrasting the level of difference within and between subspecies.

I'll do this with a mixed model framework approach (and analyze with ANOVA, a method to partition the variance of subset.)

```{r mixed.model, echo=FALSE}

#build mixed model

#run simulations for accounting for sampling error

### Subspecies examples / Data

list the strains/data used 
Mouse average MLH1 counts,

### Male Specific results

Not all strains have female data. Here are results from all strains wih male data.

### female and male comparison

## Meiotic Error

This section reviews all the data from achiasmy and 0CO bivalents.
